Commutative character sheaves and geometric types for supercuspidal representations

### 2020-07-24 Geometric types.tex
Update Geometric types.tex

Armed with the function-sheaf dictionary for smooth group schemes over finite fields, we return to the task of geometrizing Yu type data. 
The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.
In order to use these tools we must restrict our attention to Yu type data that satisfy two technical conditions, appearing in Section~\ref{ssec:geotypes} as Hypotheses~\ref{H0} and \ref{H1}. 
Granting these hypotheses, these pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
With this theorem, we provide all of the ingredients needed to geometrize a class of supercuspidal representations of arbitrary depth.

@@

We may now revisit the ingredients in the construction of the representation $\rho$ of $\underline{G}(R)$ along the lines indicated by Yu and recalled in Section~\ref{ssec:review}.
\begin{enumerate}
\labitem{M0}{M0}
The compact groups $\oK^i$ appearing in \ref{Y0} have been replaced by the smooth group schemes $\underline{G}^i$.
\labitem{M1}{M1}
The continuous representation $\orho^0$ of $\oK^0$ appearing in \ref{Y1} may be interpreted as a representation of $\underline{G}^0(R)$ obtained by inflation along $\underline{G}^0(R) \to \underline{G}^0(\Fq)$ from a representation $\varrho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$ \todo{why can $\varrho_0$ be obtained by pulling back a representation $\varrho_0^\reductive$} along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
\labitem{M2}{M2} The quasicharacters $\varphi^i$ appearing in \ref{Y2} are now quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots, d$.
In fact, if $r_i$ is the level of $\varphi^i$, as it appears in Section~\ref{ssec:quasicharacters}, then $\varphi^i$ is obtained by pulling back a quasicharacter $\varphi_i\ceq \varphi^i_{r_i}$ of the smooth group scheme $G_i\ceq G^i_{r_i} \ceq \Gr_{r_i}^{R}(\underline{G}^i)$ along $G^i \to G_i$.
\labitem{M3}{M3}
Diagram \eqref{eq:semiprod} in \ref{Y3} is now replaced by the following diagram of smooth group schemes over $R$.
\begin{equation}\label{eq:pimodel}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \underline{G}^{i}\times_{\underline{G}} \underline{J}^{i+1}\arrow{d} && \\
1 \arrow{r} & \underline{J}^{i+1} \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{d} \arrow{r} & \underline{G}^i \arrow{r} & 1\\
&& \underline{G}^{i+1} \arrow{d} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
\labitem{M4}{M4}
The representation $h_{i+1}^*(W_{i+1})$ appearing in \ref{Y4} is now obtained by pulling back a representation along 
\[
(\underline{G}^i \ltimes \underline{J}^{i+1})(R) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
\]
Let $w_{i+1}$ be that representation of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq) = (\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq)(\Fq)$. 
Then $w_{i+1}$ is itself obtained by pulling back the representation $W_{i+1}$ along the $\Fq$-points of the quotient
\[
\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq \to 
\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp.
\]
\end{enumerate}

@@

As we recalled in Section~\ref{ssec:review}, a Yu type datum consists of compact groups $\oK^i$, a representation $\orho^0$ of $\oK^0$ and quasicharacters $\varphi^i$ of $\oK^i$, for $i=0,\ldots, d$; see \ref{Y0}, \ref{Y1} and \ref{Y2}.
In Section~\ref{ssec:review} we also saw how a Yu type datum determines smooth group schemes $\underline{G}^i$, a representation $\varrho_0\red$ of the reductive quotient $(\underline{G}^0)\red_{k}$ of the special fibre $\underline{G}^0_{k}$ of $\underline{G}^0$, and quasicharacters $\varphi_i$ of the group of $k$-rational points on the level-$r_i$ Greenberg transform $G_i$ of $\underline{G}^i$; see \ref{M0}, \ref{M1} and \ref{M2}.
%
Theorem~\ref{thm:geotypes} places the following conditions on the Yu type datum:
\begin{enumerate}
\labitem{H0}{H0} the geometric component group of $(\underline{G}^0)\red_{k}$ is cyclic;
\labitem{H1}{H1} for each $i=0,\ldots, d$, either
\begin{enumerate}
\labitem{H1(a)}{H1a} $G_i$ is reductive with cyclic geometric component group, or
\labitem{H1(b)}{H1b} the quasicharacter $\varphi_i$ of $G_i$ is trivial on  $G_{i,\operatorname{der}}(k)$. \todo{It would be worth to provide an example of supercuspidal representation (with positive depth) of a non-commutative p-adic group for which the hypothesis H1(b) is satsified}
\end{enumerate}
\end{enumerate}
Hypothesis~\ref{H0} will allow us to use Lusztig's character sheaves to geometrize the character of the representation of $\orho^0$.
Hypothesis~\ref{H1a} may be used to geometrize each quasicharacter $\varphi_i$ using $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$.
Alternatively, Hypothesis~\ref{H1b} allows us to use Proposition~\ref{prop:quasicharacters} to geometrize each quasicharacter $\varphi_i$ using local systems on $G_i$, or more precisely, using commutative character sheaves on $G_i$.
Using Sections~\ref{ssec:equivariant} and \ref{ssec:LCS} we see that, in both cases, the resulting geometrization may be interpreted as an element in $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$.
Note that when Hypothesis~\ref{H1b} applies, it provides a considerably simpler geometrization than when Hypothesis~\ref{H1a} applies.

We remark that if Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then Hypothesis~\ref{H0} can be removed and Hypothesis~\ref{H1a} can be replaced with the hypothesis that each $G_i$ is reductive.

\begin{theorem}\label{thm:geotypes}
Let $(\oK^i, \orho^0, \varphi^i,d)$ be a Yu type datum that satisfies Hypotheses~\ref{H0} and \ref{H1}, and let $\orho_i$ be the representation of $\oK^i$ constructed from it in Section~\ref{ssec:review}.  Then for each $i=0,\dots, d$ there is an element $\cs{F}_i \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G^i}(G^i;\EE)$ such that
\[
\trFrob{\cs{F}_i} = \trace(\orho_i).
\]
\end{theorem}

\begin{proof}
%For every $i=0, \ldots ,d$, set $G^i = \Gr_{R}(\underline{G}^i)$.
Recall that $G^i(\Fq) = \underline{G}^i(R) = \oK^i$, canonically.
Let $r_i$ be the level of $\varphi^i$ as defined in Section~\ref{ssec:quasicharacters}. \todo{the precise reference in the series of Lusztig articles on character sheaves on disconnected groups must be provided.}
Set $r = \max\{ r_i \tq i=0, \ldots ,d\}$.

By \cite{lusztig:disconnected4}*{Thm. 21.21}, there is $A \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,(\underline{G}^0)_\Fq\red}((\underline{G}^0)_\Fq\red;\EE)$ such that 
%${\bar A}$ is a rational virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
\[
\trFrob{A} = \trace \varrho_0^\reductive.
\]
This uses Hypothesis~\ref{H0}.
%
Let $A^0\in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,(\underline{G}^0)_\Fq}((\underline{G}^0)_\Fq;\EE)$ be obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then 
\[
\trFrob{A^0} = \trace \varrho_0.
\]
The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $Q^0 = \Gr^{R}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}. 
With $r\in \NN$ as above, let ${A}_r^0$ be the equivariant Weil sheaf on the algebraic group $G_r^i$ obtained by pull-back from $A^0$ along the affine morphism $G_r^i \to Q^0$.
Factor
\begin{equation}\label{eqn:tracerho}
\begin{tikzcd}
G^0(\Fq) \arrow{rr}{\trace(\orho^0)} \arrow{rd} && \EE \\
& G_r^0(\Fq) \arrow{ru}[swap]{\trace(\orho^0)_r} 
\end{tikzcd}
\end{equation}
Observe that $\trace(\orho^0)_r$ may be recovered from ${A}_r^0$:
\[
\trFrob{{A}^0_r} = \trace(\orho^0)_r
\]

@@

We now define $\cs{A}^i_r  \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G^i_r}$ for $i=0,\ldots ,d$ recursively, following the construction of the representations $\orho^i$, as reviewed in Section~\ref{ssec:review}.
First, set $\cs{A}_r^0 = A_r^0$ and note that \eqref{eqn:tracerho} commutes with $\trace(\orho^0)_r$ replaced by $\trFrob{\cs{A}_r^0}$.
Using Hypothesis~\ref{H1}, let $\cs{L}_i$ be the geometrization of the quasicharacter $\varphi_i \ceq \varphi^i_{r_i}$ appearing in \ref{M2}.
If \ref{H1a} applies, then $\cs{L}_i \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_i}(G_i;\EE)$, using \cite{lusztig:disconnected4}*{Thm. 21.21};
if \ref{H1b} applies, then $\cs{L}_i\in \CCS(G_i)$, using Proposition~\ref{prop:quasicharacters}. \todo{provide exact reference}
In either case, $\cs{L}_i\in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_i}(G_i;\EE)$ and
\[
\trFrob{\cs{L}_i} = \varphi_i.
\]
For each $i$, let $\cs{L}^i_{r}$ be the pull-back of $\cs{L}_i$ along $G^i_{r} \to G_i$; then $\cs{L}^i_{r}$ is a linear character sheaf and
\[
\trFrob{\cs{L}^i_{r}} = \varphi^i_{r}.
\]
Now, suppose $\cs{A}^i_r$ on $G_r^i$ is defined such that
\[
\begin{tikzcd}
G^i(\Fq) \arrow{rr}{\trace(\orho^i)} \arrow{rd} && \EE\\
& G_r^i(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_r^i}} & 
\end{tikzcd}
\]
commutes.
Applying the Greenberg functor $\Gr^{R}_r$ to \eqref{eq:pimodel} gives
\begin{equation}\label{eq:pi}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && G_r^{i}\times_{G_r} J_r^{i+1} \arrow{d} && \\
1 \arrow{r} & J_r^{i+1} \arrow{r} & G_r^i \ltimes J_r^{i+1} \arrow{d}{\pi_r^{i+1}} \arrow{r}{p_r^{i}} & G_r^i \arrow{r} & 1\\
&& G_r^{i+1} \arrow{d} && \\
&& 1 && 
\end{tikzcd}
\end{equation}
where $J_r^{i+1} \ceq \Gr^{R}_r(\underline{J}^{i+1})$ and $G_r^{i} \ceq \Gr^{R}_r(\underline{G}^{i})$.
By \cite{bertapelle-gonzales:Greenberg}*{Prop 14.2}, the sequences are exact.
Consider $\cs{B}_r^{i+1}\in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_r^{i}\ltimes J_r^{i+1}}(G_r^{i}\ltimes J_r^{i+1};\EE)$ defined by
\[
\cs{B}_r^{i+1} \ceq \cs{K}_r^{i+1} \otimes (p_r^{i})^*(\cs{A}_r^{i}\otimes \cs{L}_r^{i}).
\]
Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_r^{i+1}}$ is precisely the function obtained by factoring the character of $\orho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_r)$ using the canonical identification $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_r)$. 
In particular, $\trFrob{\cs{B}^{i+1}_r}$ is constant on $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$, taking the value $\dim \orho^{i+1}$.
With reference to the morphism $\pi_r^{i+1} : G_r^i \ltimes J_r^{i+1} \to G_r^{i+1}$ from \eqref{eq:pi}, define 
\[
\cs{C}_r^{i+1} \ceq (\pi_r^{i+1})_! (\cs{B}_r^{i+1}).
\]
Then $\cs{C}_r^{i+1}\in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_r^{i+1}}(G_r^{i+1};\EE)$ and
\begin{eqnarray*}
\trFrob{\cs{C}^{i+1}_r}(x)
&=& \sum_{y\in (\pi_r^{i+1})^{-1}(x)}  \trFrob{\cs{B}_r^{i+1}}(y).
\end{eqnarray*}
Since $\trFrob{\cs{B}^{i+1}_r}$ is constant on $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$, it follows that 
\[
\trFrob{\cs{C}^{i+1}_r} = n \trFrob{\cs{B}^{i+1}_r}
\]
on $G_r^{i+1}(\Fq)$ with $n$ equal to the product of $\# (G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$ and $\dim \orho^{i+1}$.
Let $\cs{A}_r^{i+1}$ be the element of $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_r^{i+1}}(G_r^{i+1};\EE)$ given by $\cs{A}_r^{i+1} = \frac{1}{n} \cs{C}_r^{i+1}$. 
%
This completes the inductive definition of $\cs{A}_r^i$ so that the following diagram commutes.
\[
\begin{tikzcd}
G^{i+1}(\Fq) \arrow{rr}{\trace(\orho^{i+1})} \arrow{rd} && \EE\\
& G_r^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_r^{i+1}}} } & 
\end{tikzcd}
\]

>>>>

Armed with the function-sheaf dictionary for smooth group schemes over finite fields, we return to the task of geometrizing Yu type data. 
The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.
In order to use these tools we must restrict our attention to Yu type data that satisfy a technical condition, appearing in Section~\ref{ssec:geotypes} as Hypothesis~\ref{H1}. 
Granting this hypothesis, these pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
With this theorem, we provide all of the ingredients needed to geometrize a class of supercuspidal representations of arbitrary depth.

@@

We may now revisit the ingredients in the construction of the representation $\rho$ of $\underline{G}(R)$ along the lines indicated by Yu and recalled in Section~\ref{ssec:review}.
\begin{enumerate}
\labitem{M0}{M0}
The compact groups $\oK^i$ appearing in \ref{Y0} have been replaced by the smooth group schemes $\underline{G}^i$.
\labitem{M1}{M1}
The continuous representation $\orho^0$ of $\oK^0$ appearing in \ref{Y1} may be interpreted as a representation of $\underline{G}^0(R)$ obtained by inflation along $\underline{G}^0(R) \to \underline{G}^0(\Fq)$ from a representation $\varrho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$; this is a consequence of \cite{Yu:models}*{\S 10.5 (i)}.
%\todo{why can $\varrho_0$ be obtained by pulling back a representation $\varrho_0^\reductive$} along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$ 
\labitem{M2}{M2} The quasicharacters $\varphi^i$ appearing in \ref{Y2} are now quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots, d$.
In fact, if $r_i$ is the level of $\varphi^i$, as it appears in Section~\ref{ssec:quasicharacters}, then $\varphi^i$ is obtained by pulling back a quasicharacter $\varphi_i\ceq \varphi^i_{r_i}$ of the smooth group scheme $G_i\ceq G^i_{r_i} \ceq \Gr_{r_i}^{R}(\underline{G}^i)$ along $G^i \to G_i$.
\labitem{M3}{M3}
Diagram \eqref{eq:semiprod} in \ref{Y3} is now replaced by the following diagram of smooth group schemes over $R$.
\begin{equation}\label{eq:pimodel}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \underline{G}^{i}\times_{\underline{G}} \underline{J}^{i+1}\arrow{d} && \\
1 \arrow{r} & \underline{J}^{i+1} \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{d} \arrow{r} & \underline{G}^i \arrow{r} & 1\\
&& \underline{G}^{i+1} \arrow{d} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
\labitem{M4}{M4}
The representation $h_{i+1}^*(W_{i+1})$ appearing in \ref{Y4} is now obtained by pulling back a representation along 
\[
(\underline{G}^i \ltimes \underline{J}^{i+1})(R) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
\]
Let $w_{i+1}$ be that representation of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq) = (\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq)(\Fq)$. 
Then $w_{i+1}$ is itself obtained by pulling back the representation $W_{i+1}$ along the $\Fq$-points of the quotient
\[
\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq \to 
\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp.
\]
\end{enumerate}

@@

As we recalled in Section~\ref{ssec:review}, a Yu type datum consists of compact groups $\oK^i$, a representation $\orho^0$ of $\oK^0$ and quasicharacters $\varphi^i$ of $\oK^i$, for $i=0,\ldots, d$; see \ref{Y0}, \ref{Y1} and \ref{Y2}.
In Section~\ref{ssec:review} we also saw how a Yu type datum determines smooth group schemes $\underline{G}^i$, a representation $\varrho_0\red$ of the reductive quotient $(\underline{G}^0)\red_{k}$ of the special fibre $\underline{G}^0_{k}$ of $\underline{G}^0$, and quasicharacters $\varphi_i$ of the group of $k$-rational points on the level-$r_i$ Greenberg transform $G_i$ of $\underline{G}^i$; see \ref{M0}, \ref{M1} and \ref{M2}.
%
Theorem~\ref{thm:geotypes} places the following conditions on the Yu type datum:
\begin{enumerate}
%\labitem{H0}{H0} the geometric component group of $(\underline{G}^0)\red_{k}$ is cyclic;
\labitem{H1}{H1} for each $i=0,\ldots, d$, either
\begin{enumerate}
\labitem{H1(a)}{H1a} $G_i$ is reductive, or % with cyclic geometric component group, or
\labitem{H1(b)}{H1b} the quasicharacter $\varphi_i$ of $G_i$ is trivial on  $G_{i,\operatorname{der}}(k)$. \todo{It would be worth to provide an example of supercuspidal representation (with positive depth) of a non-commutative p-adic group for which the hypothesis H1(b) is satsified}
\end{enumerate}
\end{enumerate}
%Hypothesis~\ref{H0} will allow us to use Lusztig's character sheaves to geometrize the character of the representation of $\orho^0$.
Hypothesis~\ref{H1a} may be used to geometrize each quasicharacter $\varphi_i$ using $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$.
Alternatively, Hypothesis~\ref{H1b} allows us to use Proposition~\ref{prop:quasicharacters} to geometrize each quasicharacter $\varphi_i$ using local systems on $G_i$, or more precisely, using commutative character sheaves on $G_i$.
Using Sections~\ref{ssec:equivariant} and \ref{ssec:LCS} we see that, in both cases, the resulting geometrization may be interpreted as an element in $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$.
Note that when Hypothesis~\ref{H1b} applies, it provides a considerably simpler geometrization than when Hypothesis~\ref{H1a} applies.

%We remark that if Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then Hypothesis~\ref{H0} can be removed and Hypothesis~\ref{H1a} can be replaced with the hypothesis that each $G_i$ is reductive.

\begin{theorem}\label{thm:geotypes}
Let $(\oK^i, \orho^0, \varphi^i,d)$ be a Yu type datum that satisfies Hypotheses~%\ref{H0} and 
\ref{H1}, and let $\orho_i$ be the representation of $\oK^i$ constructed from it in Section~\ref{ssec:review}.  Then for each $i=0,\dots, d$ there is an element $\cs{F}_i \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G^i}(G^i;\EE)$ such that
\[
\trFrob{\cs{F}_i} = \trace(\orho_i).
\]
\end{theorem}

\begin{proof}
%For every $i=0, \ldots ,d$, set $G^i = \Gr_{R}(\underline{G}^i)$.
Recall that $G^i(\Fq) = \underline{G}^i(R) = \oK^i$, canonically.
Let $r_i$ be the level of $\varphi^i$ as defined in Section~\ref{ssec:quasicharacters}. 
%\todo{the precise reference in the series of Lusztig articles on character sheaves on disconnected groups must be provided.}
Set $r = \max\{ r_i \tq i=0, \ldots ,d\}$.

By \cite{lusztig:disconnected4}*{Thm. 21.21}, there is $A \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,(\underline{G}^0)_\Fq\red}((\underline{G}^0)_\Fq\red;\EE)$ such that 
%${\bar A}$ is a rational virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
\[
\trFrob{A} = \trace \varrho_0^\reductive.
\]
%This uses Hypothesis~\ref{H0}.
%
Let $A^0\in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,(\underline{G}^0)_\Fq}((\underline{G}^0)_\Fq;\EE)$ be obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then 
\[
\trFrob{A^0} = \trace \varrho_0.
\]
The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $Q^0 = \Gr^{R}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}. 
With $r\in \NN$ as above, let ${A}_r^0$ be the equivariant Weil sheaf on the algebraic group $G_r^i$ obtained by pull-back from $A^0$ along the affine morphism $G_r^i \to Q^0$.
Factor
\begin{equation}\label{eqn:tracerho}
\begin{tikzcd}
G^0(\Fq) \arrow{rr}{\trace(\orho^0)} \arrow{rd} && \EE \\
& G_r^0(\Fq) \arrow{ru}[swap]{\trace(\orho^0)_r} 
\end{tikzcd}
\end{equation}
Observe that $\trace(\orho^0)_r$ may be recovered from ${A}_r^0$:
\[
\trFrob{{A}^0_r} = \trace(\orho^0)_r
\]

@@

We now define $\cs{A}^i_r  \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G^i_r}$ for $i=0,\ldots ,d$ recursively, following the construction of the representations $\orho^i$, as reviewed in Section~\ref{ssec:review}.
First, set $\cs{A}_r^0 = A_r^0$ and note that \eqref{eqn:tracerho} commutes with $\trace(\orho^0)_r$ replaced by $\trFrob{\cs{A}_r^0}$.
Using Hypothesis~\ref{H1}, let $\cs{L}_i$ be the geometrization of the quasicharacter $\varphi_i \ceq \varphi^i_{r_i}$ appearing in \ref{M2}.
If \ref{H1a} applies, then $\cs{L}_i \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_i}(G_i;\EE)$, using \cite{lusztig:disconnected4}*{Thm. 21.21};
if \ref{H1b} applies, then $\cs{L}_i\in \CCS(G_i)$, using Proposition~\ref{prop:quasicharacters}. 
%\todo{provide exact reference}
In either case, $\cs{L}_i\in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_i}(G_i;\EE)$ and
\[
\trFrob{\cs{L}_i} = \varphi_i.
\]
For each $i$, let $\cs{L}^i_{r}$ be the pull-back of $\cs{L}_i$ along $G^i_{r} \to G_i$; then $\cs{L}^i_{r}$ is a linear character sheaf and
\[
\trFrob{\cs{L}^i_{r}} = \varphi^i_{r}.
\]
Now, suppose $\cs{A}^i_r$ on $G_r^i$ is defined such that
\[
\begin{tikzcd}
G^i(\Fq) \arrow{rr}{\trace(\orho^i)} \arrow{rd} && \EE\\
& G_r^i(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_r^i}} & 
\end{tikzcd}
\]
commutes.
Applying the Greenberg functor $\Gr^{R}_r$ to \eqref{eq:pimodel} gives
\begin{equation}\label{eq:pi}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && G_r^{i}\times_{G_r} J_r^{i+1} \arrow{d} && \\
1 \arrow{r} & J_r^{i+1} \arrow{r} & G_r^i \ltimes J_r^{i+1} \arrow{d}{\pi_r^{i+1}} \arrow{r}{p_r^{i}} & G_r^i \arrow{r} & 1\\
&& G_r^{i+1} \arrow{d} && \\
&& 1 && 
\end{tikzcd}
\end{equation}
where $J_r^{i+1} \ceq \Gr^{R}_r(\underline{J}^{i+1})$ and $G_r^{i} \ceq \Gr^{R}_r(\underline{G}^{i})$.
By \cite{bertapelle-gonzales:Greenberg}*{Prop 14.2}, the sequences are exact.
Consider $\cs{B}_r^{i+1}\in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_r^{i}\ltimes J_r^{i+1}}(G_r^{i}\ltimes J_r^{i+1};\EE)$ defined by
\[
\cs{B}_r^{i+1} \ceq \cs{K}_r^{i+1} \otimes (p_r^{i})^*(\cs{A}_r^{i}\otimes \cs{L}_r^{i}).
\]
Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_r^{i+1}}$ is precisely the function obtained by factoring the character of $\orho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_r)$ using the canonical identification $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_r)$. 
In particular, $\trFrob{\cs{B}^{i+1}_r}$ is constant on $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$, taking the value $\dim \orho^{i+1}$.
With reference to the morphism $\pi_r^{i+1} : G_r^i \ltimes J_r^{i+1} \to G_r^{i+1}$ from \eqref{eq:pi}, define 
\[
\cs{C}_r^{i+1} \ceq (\pi_r^{i+1})_! (\cs{B}_r^{i+1}).
\]
Then $\cs{C}_r^{i+1}\in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_r^{i+1}}(G_r^{i+1};\EE)$ and
\begin{eqnarray*}
\trFrob{\cs{C}^{i+1}_r}(x)
&=& \sum_{y\in (\pi_r^{i+1})^{-1}(x)}  \trFrob{\cs{B}_r^{i+1}}(y).
\end{eqnarray*}
Since $\trFrob{\cs{B}^{i+1}_r}$ is constant on $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$, it follows that 
\[
\trFrob{\cs{C}^{i+1}_r} = n \trFrob{\cs{B}^{i+1}_r}
\]
on $G_r^{i+1}(\Fq)$ with $n$ equal to the product of $\# (G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$ and $\dim \orho^{i+1}$.
Let $\cs{A}_r^{i+1}$ be the element of $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_r^{i+1}}(G_r^{i+1};\EE)$ given by $\cs{A}_r^{i+1} = \frac{1}{n} \cs{C}_r^{i+1}$. 
%
This completes the inductive definition of $\cs{A}_r^i$ so that the following diagram commutes.
\[
\begin{tikzcd}
G^{i+1}(\Fq) \arrow{rr}{\trace(\orho^{i+1})} \arrow{rd} && \EE\\
& G_r^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_r^{i+1}}} } & 
\end{tikzcd}
\]
